### 2015-06-30 thesis/thesis/chap6/chap6.tex
changes

\begin{itemize}
\item K. Sultan, J. Bentahar, M. El-Menshawy, "Model Checking Probabilistic Social Commitments for Intelligent Agent Communication", Journal of Applied Soft Computing, Elsevier, 2014.

\item K. Sultan, J. Bentahar, W. Wan, F. Al-Saqqar, "Modeling and Verifying Probabilistic Multi-  Agent Systems using Knowledge and Social Commitments", Journal of Expert Systems with Applications, Elsevier, 2014.

\item F. Al-Saqqar, J. Bentahar, K. Sultan, M. El-Menshawy, "On the Interaction between Knowledge and Social Commitments in Multi-Agent Systems", Applied Intelligence Journal, Springer, 2014.

\item F. Al-Saqqar, J. Bentahar, K. Sultan, W. Wan, E. Khosrowshahi
Asl, "Model Checking Temporal Knowledge and Commitments in Multi-Agent Systems Using Reduction", Simulation Modeling Practice and Theory Journal, Elsevier, 2015.
\end{itemize}

@@

\begin{itemize}

\item K. Sultan, J. Bentahar, O. Marey, "A Probabilistic Logic to Reason about the Interaction between Knowledge and Social Commitments in MASs", In the Proc. of The 13th International Conference on Intelligent Software Methodologies, Tools, and Techniques (SOMET\_14), Langkawi, Malaysia, 2014.

\item M. Mbarki, O. Marey, J. Bentahar, K. Sultan,  "Agent Types and Adaptive Negotiation Strategies in Argumentation-Based Negotiation", In the Proc. of the IEEE International Conference on Tools with Artificial Intelligence (ICTAI), Limassol, Cyprus, 2014.

\item K. Sultan, M. El-Menshawy, J. Bentahar, "Reasoning about Social Commitments in the Presence of Uncertainty", In the Proc. of The 12th International Conference on Intelligent Software Methodologies, Tools, and Techniques (SOMET\_13), Budapest, Hungary, 2013.
\end{itemize}

@@

\begin{itemize}
\item K. Sultan, J. Bentahar, R. Mizouni, "Model Checking the Interaction Between Individual and Group Knowledge and Commitments in Probabilistic Multi-Agent Systems", Engineering Applications of Artificial Intelligence, Elsevier, (submitted: August 2014).
\item O. Marey, J. Bentahar, E. Khosrowshahi Asl, K. Sultan, R. Dssouli, "Decision Making under Subjective Uncertainty in Argumentation-Based Negotiation.  Ambient Intelligence and Humanized Computing, (submitted: November 2014).
\end{itemize}

>>>>

\begin{itemize}
\item E. Khosrowshahi Asl, J. Bentahar, H. Otrok, R. Mizouni, "Efficient Coalition Formation for Web Services", IEEE Transactions on Services Computing, 2015.

\item E. Khosrowshahi Asl, J. Bentahar, H. Otrok, B. Khosravifar, R. Mizouni, "To compete or cooperate? This is the question in communities of autonomous services", Journal of Expert Systems with Applications, Elsevier, 2014.

\end{itemize}

@@

\begin{itemize}
\item E. Khosrowshahi Asl, J. Bentahar, H. Otrok, R. Mizouni, "Efficient Community Formation for Web Services",  IEEE SCC, Santa Clara, CA, USA, 2013.

\end{itemize}

@@

\begin{itemize}
\item E. Khosrowshahi Asl, J. Bentahar, H. Otrok, R. Mizouni, "Distributed Decision Making for Dynamic Formation of Web Services Communities", Decision Support Systems, Elsevier (Submitted: June, 2015).
\end{itemize}
